Query Optimization for Dynamic Imputation

### 2017-05-15 paper/algorithm.tex
reference fixes, small changes

The space of query plans is similar to that considered in a canonical
cost-based optimizer~\cite{blasgen1981system}, with the addition of imputation operators appearing before and after traditional operators.
\Cref{fig:query-schematic} shows a plan schematic for a query involving three tables, absent any imputation operators.

@@

\subsubsection{Pareto-optimal plans}
Given a query, \ProjectName{} produces a final set of query plans $Q$ by only keeping plans that are not dominated by others in the search space. So for a search space $S$, \[Q= \{ q ~|~ \not\exists q' \in S.\ q \neq q' \land \doms{q'}{q} \}.\]

@@

\subsubsection{Decision trees}

@@

\subsubsection{Mean}

>>>>

The space of query plans is similar to that considered in a canonical
cost-based optimizer~\cite{blasgen1981system}, with the addition of imputation operators appearing before and after traditional operators.
\Cref{fig:query-schematic} shows a plan schematic for a query involving three tables, absent any imputation operators. Plans produced by \ProjectName{} can mix both \textit{Impute} and \textit{Drop}
operators.

@@

\subsubsection{Pareto-optimal plans}\label{subsubsec:pareto}
Given a query, \ProjectName{} produces a final set of query plans $Q$ by only keeping plans that are not dominated by others in the search space. So for a search space $S$, \[Q= \{ q ~|~ \not\exists q' \in S.\ q \neq q' \land \doms{q'}{q} \}.\]

@@

\subsubsection{Decision trees}\label{subsubsec:decision-trees}

@@

\subsubsection{Mean}\label{subsubsec:mean}

### 2017-05-15 paper/examples.tex
reference fixes, small changes

\caption{The operators $\sigma$, $\pi$, $\bowtie$, and $g$ are the standard relational selection, projection, join, and group-by/aggregate, $\mu$ and $\delta$ are specialized imputation operators (\Cref{sec:operators}). The imputation operators are highlighted.}
\end{figure}

>>>>

\caption{The operators $\sigma$, $\pi$, $\bowtie$, and $g$ are the standard relational selection, projection, join, and group-by/aggregate, $\mu$ and $\delta$ are specialized imputation operators (\Cref{sec:operators}), and
can be mixed throughout a plan. The imputation operators are highlighted.}
\label{fig:example-plans}
\end{figure}
